\bf Range Analysis for the IonMonkey JavaScript engine

### 2012-05-02 project-writings/paper.tex
typo

\section{Related Work}
%% XXX: FIXME, TODO
There are a variety of approaches to range analysis. A recent work, ``The Design
and Implementation of a Non-Iterative Range Analysis Algorithm on a
Production Compiler'', by Teixeira and Pereira, outlines a practical implementation of
implementation of an algorithm designed by by Su and Wagner
\cite{Su04aclass}. The algorithm due to Su and Wagner is
non-iterative, and works by constructing a constraint graph from the program's control flow graph.

>>>>

\section{Related Work}
%% XXX: FIXME, TODO
There are a variety of approaches to range analysis. A recent work, ``The Design
and Implementation of a Non-Iterative Range Analysis Algorithm on a
Production Compiler'', by Teixeira and Pereira, outlines a practical implementation of
implementation of an algorithm designed by Su and Wagner
\cite{Su04aclass}. The algorithm due to Su and Wagner is
non-iterative, and works by constructing a constraint graph from the program's control flow graph.
